Annotated example of index standardization with VAST

### 2021-12-09 doc/appendix-pcod-VAST-tweedie.Rmd
fix formatting

```{r packages, message=FALSE, warning=FALSE, cache=FALSE}
library(TMB)
library(VAST)
library(sp)
library(sdmTMB)
library(here)
```

@@

```{r fit, echo = TRUE, results = 'hide'}
 # create folder for saved output:
dir.create(paste0(here("doc", "appendix-VAST-tweedie")), showWarnings = FALSE)

@@

```{r save-plots, echo = TRUE, warning = FALSE}
plot(
  fit,
  check_residuals = FALSE,
  working_dir = paste0(here("doc", "appendix-VAST-tweedie"), "/")
)
```

@@

```{r plot-density, echo = TRUE}
knitr::include_graphics(here("doc", "appendix-VAST-tweedie", "ln_density-predicted.png"))
```

@@

```{r plot-index, echo = TRUE, out.width="3in"}
if (file.exists(here("doc", "appendix-VAST-tweedie", "Index-Biomass.png"))) {
  knitr::include_graphics(here("doc", "appendix-VAST-tweedie", "Index-Biomass.png"))
}
if (file.exists(here("doc", "appendix-VAST-tweedie", "Index.png"))) {
  knitr::include_graphics(here("doc", "appendix-VAST-tweedie", "Index.png"))
}
```

>>>>

```{r packages, message = FALSE, warning = FALSE, cache = FALSE}
library(TMB)
library(VAST)
library(sp)
library(sdmTMB)
library(here)
```

@@

```{r fit, echo = TRUE, results = FALSE, message = FALSE, warning = FALSE}
 # create folder for saved output:
dir.create(paste0(here("doc", "appendix-VAST-tweedie")), showWarnings = FALSE)

@@

```{r save-plots, echo = TRUE, message = FALSE, warning = FALSE}
plot(
  fit,
  check_residuals = FALSE,
  working_dir = paste0(here("doc", "appendix-VAST-tweedie"), "/")
)
```

@@

```{r plot-density, echo = TRUE, out.width = "6in"}
knitr::include_graphics(here("doc", "appendix-VAST-tweedie", "ln_density-predicted.png"))
```

@@

```{r plot-index, echo = TRUE, out.width = "3in"}
if (file.exists(here("doc", "appendix-VAST-tweedie", "Index-Biomass.png"))) {
  knitr::include_graphics(here("doc", "appendix-VAST-tweedie", "Index-Biomass.png"))
}
if (file.exists(here("doc", "appendix-VAST-tweedie", "Index.png"))) {
  knitr::include_graphics(here("doc", "appendix-VAST-tweedie", "Index.png"))
}
```
